---
output:
  md_document:
    variant: markdown_github
---
![License](https://img.shields.io/:license-mit-blue.svg)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Package `marketconf`: Stock Market Confidence Indexes

The R package `marketconf` reads **U. S. Stock Market Confidence Indexes**
data from [Yale School of Management's International Center for Finance](https://som.yale.edu/faculty-research/our-centers-initiatives/international-center-finance/data/stock-market-confidence) web page.

The four U.S. Stock market confidence indexes are derived, monthly, from
survey data on the behavior of investors, these indexes are:

* __US1YI__: [U.S. One Year Index](https://som.yale.edu/faculty-research/our-centers-initiatives/international-center-finance/data/stock-market-confidence-indices/united-states-one-year-index)

* __USVI__: [U.S. Valuation Index](https://som.yale.edu/faculty-research/our-centers-initiatives/international-center-finance/data/stock-market-confidence-indices/united-states-valuation-index)

* __USBODI__: [U.S. Buy-On-Dips Confidence Index](https://som.yale.edu/faculty-research/our-centers-initiatives/international-center-finance/data/stock-market-confidence-indices/united-states-buy-dips-confidence-index)

* __USCI__: [U.S. Crash Confidence Index](https://som.yale.edu/faculty-research/our-centers-initiatives/international-center-finance/data/stock-market-confidence-indices/us-crash-confidence-index)

## Package installation

```{r, eval=FALSE}
library(devtools)
devtools::install_github("EnriquePH/marketconf")
```

## Example

This is a basic example which plots __U.S. Valuation Index__:

```{r example}
library(marketconf)
library(ggplot2)

index_df <- get_index("USVI")

ggplot(index_df, aes(x = Date, y = USVI.Value, color = Investor)) +
  geom_line()
```

## License

The `markerconf` package is under the **MIT License (MIT)**, but the 
__Stock Market Confidence Indexes__ are produced and copyrighted by the
__International Center of Finance at the Yale School of Management__.
See [TERMS OF USE](https://som.yale.edu/faculty-research/centers-initiatives/international-center-for-finance/data/stock-market-confidence-indices/stock-market-confidence-indices) at [Yale University](https://som.yale.edu/)'s web page.


