---
output:
  md_document:
    variant: markdown_github
---
![License](https://img.shields.io/:license-mit-blue.svg)
[![Build Status](https://travis-ci.org/EnriquePH/marketconf.svg?branch=master)](https://travis-ci.org/EnriquePH/marketconf)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/EnriquePH/marketconf?branch=master&svg=true)](https://ci.appveyor.com/project/EnriquePH/marketconf)
[![Donate](https://img.shields.io/badge/Donate-PayPal-green.svg)](https://www.paypal.com/cgi-bin/webscr?cmd=_s-xclick&hosted_button_id=QMR7L28X52GN2)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Package `marketconf`: Stock Market Confidence Indexes

The R package `marketconf` reads **U. S. Stock Market Confidence Indexes**
data from [Yale School of Management's International Center for Finance](https://som.yale.edu/faculty-research/our-centers-initiatives/international-center-finance/data/stock-market-confidence) web page.

This package is for stock market prediction and risk valuation, and
it can be used with other packages like [`quantmod`](https://cran.r-project.org/web/packages/quantmod/index.html), [`TTR`](https://cran.r-project.org/web/packages/TTR/index.html) or [`tidyquant`](https://cran.r-project.org/web/packages/tidyquant/index.html)

## Package installation

```{r, eval=FALSE}
library(devtools)
devtools::install_github("EnriquePH/marketconf")
```

## Examples

### List indices

The four U.S. Stock market confidence indexes are derived, monthly, from
survey data on the behavior of investors, these indexes are:

```{r}
library(marketconf)
library(knitr)
kable(US_confidence_indices())
```

### Plotting

This is a basic example which plots __U.S. Valuation Index__:

```{r example}
library(ggplot2)

index_symbol <- "USVI"
index_df <- get_index(index_symbol)

ggplot(index_df, aes(x = Date, y = USVI.Value, color = Investor)) +
  geom_line() +
  ggtitle(get_index_description(index_symbol))
```


## License

The `markerconf` package is under the **MIT License (MIT)**, but the 
__Stock Market Confidence Indexes__ are produced and copyrighted by the
__International Center of Finance at the Yale School of Management__.
See [TERMS OF USE](https://som.yale.edu/faculty-research/centers-initiatives/international-center-for-finance/data/stock-market-confidence-indices/stock-market-confidence-indices) at [Yale University](https://som.yale.edu/)'s web page.
