---
title: "Package `marketconf`: Stock Market Confidence Indexes"
author: "Enrique Pérez Herrero"
date: "08-02-2023"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Stock Market Confidence Indexes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Summary

The R package `marketconf` reads data on **U. S. Stock Market Confidence
Indexes** from [Yale School of Management's International Center for
Finance](https://som.yale.edu/faculty-research/our-centers-initiatives/international-center-finance/data/stock-market-confidence)
web page.

This package is for stock market prediction and risk valuation, and
it can be used with other packages like [`quantmod`](https://cran.r-project.org/web/packages/quantmod/index.html), [`TTR`](https://cran.r-project.org/web/packages/TTR/index.html) or [`tidyquant`](https://cran.r-project.org/web/packages/tidyquant/index.html)


# Package installation

```{r, eval=FALSE}
library(devtools)
devtools::install_github("EnriquePH/marketconf")
```

# List available indices

The four U.S. Stock market confidence indexes are derived monthly from
survey data on the investors' behevior. These indices are:

```{r}
library(marketconf)
library(knitr)
kable(US_confidence_indices())
```


# Search for index symbol description
```{r}
index_symbol <- "USBODI"
get_index_description(index_symbol)
```
# Search for index symbol information

```{r}
index_symbol <- "USBODI"
get_index_info(index_symbol)
```

# Load a given index into a `data.frame`

```{r}
index_df <- get_index(index_symbol)
kable(head(index_df))
```


# Plotting

This is a basic example that plots the __U.S. Valuation Confidence Index__:

```{r example}
library(ggplot2)

index_symbol <- "USVI"
index_df <- get_index(index_symbol)

ggplot(index_df, aes(x = Date, y = USVI.Value, color = Investor)) +
  geom_line() +
  ggtitle(get_index_description(index_symbol))
```


# License

The `markerconf` package is under the **MIT License (MIT)**, but the 
__Stock Market Confidence Indexes__ are produced and copyrighted by the
__International Center of Finance at the Yale School of Management__.
See [TERMS OF USE](https://som.yale.edu/faculty-research/centers-initiatives/international-center-for-finance/data/stock-market-confidence-indices/stock-market-confidence-indices) at [Yale University](https://som.yale.edu/)'s web page.
